---
title: "Scientific Communication Support"
subtitle: "Ecology of Animal Societies"
author: "Alie Ashbury"
date: "last updated: `r Sys.Date()`"
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
github-repo: ekopter/scientific_communication_support_website
description: "A website for info and resources related to scientific communication"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#library(icons)
knitr::opts_chunk$set(echo = TRUE,
                      comment = "#>",
                      collapse = TRUE)
knitr::opts_knit$set(root.dir = '../')
```


```{r set_fold, include=FALSE}
source("R/initial_folding.R")
create_html_header("show") # either "show" or "fold"
```



# Welcome

I'm Alie, the EAS department's Scientific Writer. My job is to support other department members in the communication of their science to scientific audiences. This includes support with everything from writing papers and grant proposals, to putting together conference presentations, to designing (and coding) data visualizations.

If you have any questions or comments, or are interested in receiving my help for something you're working on, please feel free to contact me.

`r icons::fontawesome$brands$slack` Alie  <br>

`r icons::fontawesome$solid$envelope` aashbury@ab.mpg.de  <br>

`r icons::fontawesome("map-marker-alt", style = "solid")` Bückle 5.27  <br>

This website is meant to be a source of support for those looking for assistance with their scientific communication - this is where I will compile information and resources that I regularly give/recommend to people. 

Please note, this website is still very much under construction!


## Contents {-}

The information on this website is divided into several categories:


- [Alie's Programs]: Details about the specific programs and services that I offer to department members.
- [Scientific Writing]: Lists and links of helpful resources related to scientific writing.
- [Scientific Presentations]: Coming soon!
- [Data Visualization]: Coming soon!
- Random posts: [Feedback framework](.docs/feedback-framework.html), [All About Abstracts](./Abstracts.html), more coming soon!


---

I built this website with bookdown, using the EAS template made by [Kosmas Hench](https://github.com/k-hench).