---
output: html_document
editor_options:
  chunk_output_type: console

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "#>",
                      collapse = TRUE)
knitr::opts_knit$set(root.dir = '../')
```


# Scientific Writing in the EAS Department {.unlisted .unnumbered #EASslides}

[*UNDER CONSTRUCTION :)*]

The following slides are from the workshop/discussion series about *Scientific Writing in the EAS Department* that took place during lab meetings on June 1st & 22nd, and October 19th, 2022. 


## Day 1 {-}

```{r fig.width=10, fig.height=8}
#knitr::include_graphics("https://github.com/ekopter/scientific_communication_support_website/blob/main/pdfs/Sci_Writ_EAS_series/Day_1.pdf")
```

```{r fig.width=10, fig.height=8}
#knitr::include_url("https://github.com/ekopter/scientific_communication_support_website/blob/main/pdfs/Sci_Writ_EAS_series/Day_1.pdf?raw=true")
```

```{r fig.width=10, fig.height=8}
#knitr::include_graphics("https://raw.githubusercontent.com/ekopter/scientific_communication_support_website/ef6976663560a8876acb466136f42bf8c6a546e5/pdfs/Sci_Writ_EAS_series/Day_1.pdf")

```
```{r fig.width=10, fig.height=8}
knitr::include_graphics("./pdfs/Sci_Writ_EAS_series/Day_1.pdf")
```

 

![Day 1; 01 June](./pdfs/Sci_Writ_EAS_series/Day_1.pdf){width=100% height=500px}\


<!-- ![Day 1; 01 June](https://github.com/ekopter/scientific_communication_support_website/blob/ae124975a0ab683355bc78a1f1a8f915ecafcfad/pdfs/Sci_Writ_EAS_series/Day%201.pdf){width=100% height=500px}\ -->


<!-- "https://raw.githubusercontent.com/ekopter/scientific_communication_support_website/5206927edfe7f611cf7fc701af760af0b2529d97/pdfs/Sci_Writ_EAS_series/Day%201.pdf"  -->

```{r fig.width=10, fig.height=8}
xfun::embed_file("vignettes/Sci_Writ_EAS_series/Day 1.pdf")
```

## Day 2 {-}

![Day 2; 22 June](/Users/aashbury/Documents/scientific_communication_support_website/vignettes/Sci_Writ_EAS_series/Day 2.pdf){width=100% height=500px}\

## Day 1 and 2 Group Input {-}

![Day 1&2 Group input; 01 & 22 June](/Users/aashbury/Documents/scientific_communication_support_website/vignettes/Sci_Writ_EAS_series/Day 1 group input.pdf){width=100% height=500px}

## Day 3 {-}

![Day 3; 19 Oct](/Users/aashbury/Documents/scientific_communication_support_website/vignettes/Sci_Writ_EAS_series/Day 3.pdf){width=100% height=500px}

[Back to Blog main page](#blog_main)